---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(doconv)
```

# doconv

The tool offers a set of functions for converting 'Microsoft Word' or 
'Microsoft PowerPoint' documents to 'PDF' format and also for converting 
them to images in the form of thumbnails. In order to work, 'LibreOffice' 
must be installed on the machine and possibly 'python' and 'Microsoft Word'.

<!-- badges: start -->
[![R build status](https://github.com/ardata-fr/doconv/workflows/R-CMD-check/badge.svg)](https://github.com/ardata-fr/doconv/actions)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

## Installation

You can install the latest version from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("ardata-fr/doconv")
```

You need R version `>= 4.0` to use this package.

## Example

```{r}
library(doconv)
```
## Generate thumbails from file

You can generate thumbails as an image by using `to_miniature`:

```{r}
docx_file <- system.file(package = "doconv", "doc-examples/example.docx")
to_miniature(
  filename = docx_file, 
  row = c(1, 1, 2, 2),
  use_docx2pdf = TRUE)
```

It uses 'LibreOffice' to convert Word or PowerPoint documents to PDF. It
probably works with other types of document but the package is only 
focusing on PDF, Word and PowerPoint documents. If option `use_docx2pdf=TRUE`,
[docx2pdf](https://github.com/AlJohri/docx2pdf) is used instead of 'LibreOffice'
to convert Word files to PDF; you can only use that option if 'Word' and
'docx2pdf' is installed on your machine.

## Convert a PowerPoint file to PDF

```{r}
docx_file <- system.file(package = "doconv", "doc-examples/example.pptx")
to_pdf(docx_file, output = "pptx_example.pdf")
to_miniature("pptx_example.pdf", width = 1000)
```

### Convert a Word file to PDF

```{r}
to_pdf(docx_file, output = "docx_example.pdf")
```

```{r include=FALSE}
unlink(c("docx_example.pdf", "pptx_example.pdf") )
```

## Setup

First 'LibreOffice' must be available on your machine, please visit https://www.libreoffice.org/ and follow the installation instructions.

> If 'Microsoft Word' is available on your machine, you can get images 
or pdf that looks exactly the same than the document rendered with 
'Microsoft Word', if not 'LibreOffice' is used to convert Word documents 
to PDF or as an image, in this case, be aware that 'LibreOffice' does not 
always render the document as 'Microsoft Word' would do (sections can be 
misunderstood for example). 

If 'Microsoft Word' is available on your machine, install python module 
'docx2pdf' with the command `docx2pdf_install()` (and make sure beforehand that 
python is available on your machine too):

```{r eval=FALSE}
library(locatexec)
library(doconv)
if(exec_available("python", error = TRUE) && # check that python is available
   !docx2pdf_available()){ # check that docx2pdf is available
  docx2pdf_install()
}
```

## docx2pdf and batch process

If docx2pdf process Word documents that contains TOC or any Word computed field, 
the user will be invited to confirm the operation with a Word pop-up that must be 
confirmed. That makes the process unreliable when running in non-interactive mode. 

**Then `docx2pdf` option should only be used in interactive mode when Word is available.**


## Related work

* Packages [docxtractr](http://cran.r-project.org/package=docxtractr) is providing 
`convert_to_pdf()` that works very well. The functionality integrated in Bob Rudis' 
package depends only on 'LibreOffice'. 

```{r include=FALSE}
minimage::compress_images("man/figures", "man/figures", overwrite = TRUE)
```

