---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(doconv)
```

# doconv

The tool offers a set of functions for converting Microsoft Word or 
Microsoft PowerPoint documents to PDF format and also for converting 
them to images in the form of thumbnails. In order to work, LibreOffice 
must be installed on the machine and possibly python.

<!-- badges: start -->
[![R build status](https://github.com/ardata-fr/doconv/workflows/R-CMD-check/badge.svg)](https://github.com/ardata-fr/doconv/actions)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

## Installation

You can install the latest version from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("ardata-fr/doconv")
```


## Example

```{r}
library(doconv)
```
## Generate thumbails from file

You can generate thumbails as an image by using `to_miniature`:

```{r}
docx_file <- system.file(package = "doconv", "doc-examples/bookdown.docx")
to_miniature(
  filename = docx_file, 
  row = c(1, 1, 1, 2, 2, 2),
  use_docx2pdf = TRUE)
```

It uses 'LibreOffice' to convert Word or PowerPoint documents to PDF. It
probably works with other types of document. If option `use_docx2pdf=TRUE`,
[docx2pdf](https://github.com/AlJohri/docx2pdf) is used instead of 'LibreOffice'
to convert Word files to PDF; you can only use that option if 'Word' and
'docx2pdf' is installed on your machine.

## Convert a PowerPoint file to PDF

```{r}
docx_file <- system.file(package = "doconv", "doc-examples/first_example.pptx")
to_pdf(docx_file, output = "first_example.pdf")
to_miniature("first_example.pdf", width = 750)
```

### Convert a Word file to PDF

```{r}
to_pdf(docx_file, output = "bookdown.pdf")
```

```{r include=FALSE}
unlink(c("bookdown.pdf", "first_example.pdf") )
```

## Related work

* Packages [docxtractr](http://cran.r-project.org/package=docxtractr) is providing 
`convert_to_pdf()` that works very well. 

```{r include=FALSE}
minimage::compress_images("man/figures", "man/figures", overwrite = TRUE)
```

